%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 3.0 (December 17, 2022)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Author:
% Vel (vel@latextemplates.com)
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% License:
% CC BY-NC-SA 4.0 (https://creativecommons.org/licenses/by-nc-sa/4.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
	%a4paper, % Uncomment for A4 paper size (default is US letter)
	11pt, % Default font size, can use 10pt, 11pt or 12pt
]{resume} % Use the resume class

\usepackage{ebgaramond} % Use the EB Garamond font

%------------------------------------------------

\name{Giulio Rebuffo} % Your name to appear at the top

% You can use the \address command up to 3 times for 3 different addresses or pieces of contact information
% Any new lines (\\) you use in the \address commands will be converted to symbols, so each address will appear as a single line.

\address{Zug, Gubelstrasse 7, 3000} % Main address


\address{giulio.rebuffo@gmail.com} % Contact information

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	
    \textbf{The American School In Switzerland, Lugano} \hfill \textit{2018-2022} \\ 
	AP Diploma \\
	Highest Honors Student \\
	SAT Score: 1480 \\
    AP Macroeconomics: 5/5 \\
    AP Calculus AB: 5/5 \\
    AP Calculus BC: 5/5 \\
    AP Computer Science 5/5 \\
    AP Italian: 5/5 \\
    AP Statistics: 5/5 \\

	\textbf{University Of Lugano} \hfill \textit{September 2022} \\ 
	B.S. in Computer Science \& Engineering (ongoing) \\
	
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

	\begin{rSubsection}{University Of Genoa}{2016 - 2017}{Hobbyist Embedded System Developer}{Genoa, Italy}
		\item I was allowed to do small research tasks for the robotics research team as an aspiring developer after catching one of the professor's attention,
		\item I was able to get experience with the ROS framework and get valuable experience with C++ and Python.
		\item I also built a simulation in C\# for drone path finding using the Unity 3D framework and used speech recognition in joint with my robotics knowledge.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Deepit AG}{2017-2018}{Intern Backend/Frontend/Blockchain Developer}{Genoa, Italy}
		\item Built Smart contracts for multiple platforms such as hooks for the Universal Login protocol and rewriten the POA bridge to accept Compound C-Tokens.
		\item Built frontends and wallets interfaces for customizable ERC20 tokens deployers and built a vesting hub protocol.
		\item Built and managed PostgreSQL Databases for indexing of customer's transactions.
        \item Experience with Backend-Frontend interaction of various kinds.
        \item Learnt several technologies such as Solidity, Typescript, Javascript and WebAssembly (Emscripten).
        \item Learnt several frameworks such as Truffle, Hardhat, Angular, React.
	\end{rSubsection}

%------------------------------------------------

	\begin{rSubsection}{Asset Bridging Firm I am not saying the name}{2018 - 2020}{Intern Backend Rust Developer}{Unspecified}
		\item Learnt how to manage a lot of money.
        \item Refactored the entirety of their backend.
        \item Rewritten their tools to conform their new backend version.
		\item Learnt Rust, and its best practices, along with code refactoring abilities.
		\item Learnt how large scales deployments are handled and how to act in a corporate-like environment.
	\end{rSubsection}

    \begin{rSubsection}{Erigon AG}{2021 - present}{Project Lead}{Zug, Switzerland}
		\item Implemented PoS transition within the Erigon Client, built the entirety and foundation of its consensus Engine.
		\item Bootstraped and current Project Lead of the Caplin Project.
		\item Implemented multiple still existing routines of the Silkworm Client written in C++.
        \item Created the first Rust implementation of the Ethereum jsonrpc in Akula.
        \item Currently Redesigning Ethereum as a whole within the Erigon Client.
        \item Performed basics Devop tasks such as contributing in setting up our Kubernetes testing infrastructure.
        \item Main technologies I used: Golang, Kubernetes, C++, Rust, Python, Docker.
	\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

	\begin{tabular}{@{} >{\bfseries}l @{\hspace{6ex}} l @{}}
		Programming Languages & Golang, C, C++, Rust, Python, Solidity, Javascript, Typescript \\
		Protocols \& APIs & DevP2P, LibP2P, JSON, GRPC, REST \\
		Databases & MDBX, LMDB, PostgreSQL, MongoDB \\
	\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

	%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
